\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-11-18 doc/flexiblesusy-paper.tex
slightly reformulate "Current limitations"

\subsection{Current limitations and future extensions}
Although we try to handle as many models as possible there are still
some limitations to what can be done. In it's current form \fs assumes
all couplings are are real, therefore it is limited to $CP$-conserving
versions of SUSY models.   Although it is implicit in the
title we would like to stress that currently we cannot provide a
spectrum generator for non-SUSY models.  This also means that like
other spectrum generators it is difficult to reliably predict the mass
spectrum in extreme cases such as Split-SUSY
\cite{Wells:2003tf,ArkaniHamed:2004fb,Giudice:2004tc} where the mass
scales of the SUSY model are drastically split leading to very large
logarithms which are not resummed.  In such cases the tower of
effective theories offers the best possibility for a solution.
However for this to work first \fs must be extended to include
non-SUSY models.  Finally the gauge group of the model should be
semi-simple and contain the standard model gauge group as factor so
that we can match to the SM at low energies.

Future releases which extend \fs beyond each of these limitations are
already planned.

>>>>

\subsection{Current limitations and future extensions}
Although we try to handle as many models as possible, there are still
some limitations to what can be done. In it's current form \fs assumes
all couplings are real, therefore it is limited to $CP$-conserving
versions of SUSY models.  Although it is implicit in the title, we
would like to stress that currently we cannot provide a spectrum
generator for non-SUSY models.  This also means that like other
spectrum generators it is difficult to reliably predict the mass
spectrum in extreme cases such as Split-SUSY
\cite{Wells:2003tf,ArkaniHamed:2004fb,Giudice:2004tc}, where the mass
scales of the SUSY model are drastically split, leading to very large
logarithms which are not resummed.  In such cases the tower of
effective theories offers the best possibility for a solution.
However, for this to work \fs must be extended to include non-SUSY
models.  Finally, the gauge group of the model is currently restricted
to be semi-simple and to contain the Standard Model gauge group as
factor, so that the SUSY model can be directly matched to the SM at
low energies.
%
Future releases which extend \fs beyond each of these limitations are
already planned.
